---
title: "eQTL Network Expansion"
author: "Benika Hall"
date: "February 3, 2015"
output: pdf_document
fig_caption: yes
---

```{r, echo=FALSE}

library(igraph)

#Set working directory
setwd("~/Documents/NeXTProject/")
```
Load data:
```{r network-data, cache=TRUE, }

genes <- read.table("~/Documents/NeXTProject/connected.txt", header=TRUE, sep="\t")
g=as.matrix(genes)
y <- graph.edgelist(g, directed=FALSE)
```

The spin glass algorithm requires a fully-connected network, so let's check for that.
```{r simplify, cache=TRUE}
is.connected(y)
```


Let's start the community detection process:

Parameters: 

update.rule - “simple” and “config”. “simple” uses a random graph with the same number of edges as the baseline probability and “config” uses a random graph with the same vertex degrees as the input graph.

gamma - This specifies the balance between the importance of present and non-present edges in a community.

```{r community-detection, cache=TRUE, dependson='network-data'} 
#Run the community detection algorithm
sg <- spinglass.community(y, weights = E(y)$weight, update.rule="config",start.temp=1, stop.temp=.80, gamma =2)

```


Lets look at our output from the community detection algorithm
```{r results, cache=TRUE,echo=FALSE, dependson='network-data'}
#Get community sizes
sizes(sg)

#Get node memberships
membership(sg)

#Get detected communities
communities(sg)

```

Optional: Only use communities that are not made of isolates. We should not have any if we are using spin glass.

```{r cache=TRUE}
x <- which(sizes(sg) > 1)

#Create a subgraph of those communities
sub <- induced.subgraph(y, which(membership(sg)==x))
#plot(sub)

```

Create a function that creates a table of the memberships with the names from our input.

```{r cache=TRUE}
edgelist <- tapply(seq_along(membership(sg)), membership(sg), function(xx) xx)
comList <- tapply(membership(sg), membership(sg), names)

length(comList)                         ## number of communities
comsize <- sapply(comList, length)

# vx <- induced.subgraph(neighborhood.size(y,order=8, nodes=snps)) 
# vx<- graph.neighborhood(vx, 8, snps)
# vx<-get.edgelist(vx)

bigComIndex <- which(comsize>7)

## pull out a community based on its index
coms3 <- edgelist[bigComIndex[[25]]]    

comGraphBig1 <- induced.subgraph(y, coms3[[1]])

#Create an edgelist that can be used in other analyses
c <-get.edgelist(comGraphBig1)

write.csv(c, "gamma-2-start1-stop-.8-comm-25.csv")

```

References 

J. Reichardt and S. Bornholdt: Statistical Mechanics of Community Detection, Phys. Rev. E, 74, 016110 (2006), http://arxiv.org/abs/cond-mat/0603718

M. E. J. Newman and M. Girvan: Finding and evaluating community structure in networks, Phys. Rev. E 69, 026113 (2004)

V.A. Traag and Jeroen Bruggeman: Community detection in networks with positive and negative links, http://arxiv.org/abs/0811.2329 (2008).

